Source-dependent likelihood-ratio ranking statistic for compact binary coalescence candidates

### 2016-10-20 article_rankstatsrc.tex
added updated logPj plots and Bartos citation

Currently, the likelihood ratio-based ranking statistic implemented in GstLaL assumes that gravitational-wave signals are equally likely to be recovered by any waveform template in the template bank; that is, the signal population of compact binaries is assumed to follow the placement of the waveforms in the template bank. This has been implicitly chosen in past gravitational-wave searches from compact binary coalescences in order to maximize the SNR of the signal, but it carries no astrophysical information of source population models. As a result, compact binary coalescence searches suffer in sensitivity because it assumes an incorrect distribution of compact binaries in the Universe, which yields an algorithm with less sensitivity of detecting real signals.

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{lnP_vs_rho_Ozel.pdf}
\includegraphics[width=0.5\textwidth]{lnP_vs_rho_BBH.pdf}
\caption{Lagrangian fits of $P_{jk}$ vs $\rho$ for select templates, which are different for each source population (top: BNS, bottom: BBH). Dots are the data points, and solid lines are the functions fitted with cubic splines. The $\rho$ values are found using the Chebyshev nodes, with the addition of $\rho=0$.}
\label{fig:Pvsrho}
\end{figure}

>>>>

Currently, the likelihood ratio-based ranking statistic implemented in GstLaL assumes that gravitational-wave signals are equally likely to be recovered by any waveform template in the template bank; that is, the signal population of compact binaries is assumed to follow the placement of the waveforms in the template bank. This has been implicitly chosen in past gravitational-wave searches from compact binary coalescences in order to maximize the SNR of the signal, but it carries no astrophysical information of source population models. As a result, compact binary coalescence searches suffer in sensitivity because it assumes an incorrect distribution of compact binaries in the Universe, which yields an algorithm with less sensitivity of detecting real signals. Bartos and Marka \cite{2015PhRvL.115w1101B} estimate that the inclusion of source-dependent factor will increase binary neutron star detections by 14\% for all-sky searches.

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{lnP_vs_rho_Ozel.pdf}
\includegraphics[width=0.5\textwidth]{lnP_vs_rho_BBH.pdf}
\caption{Source-dependent probability as a function of $\rho$ for select templates, which are different for each population (top: BNS, bottom: BBH). Dots are the data points, and solid lines are the functions fitted with cubic splines. The $\rho$ values are found using the Chebyshev nodes, with the addition of $\rho=0$, though the functions are only fitted to a minimum value of $\rho=4$, which is the SNR threshold.}
\label{fig:Pvsrho}
\end{figure}
